### 2017-04-09 Chapters/introduction.tex
Correct quotes, add quote to chapter 3

\textit{There's an infinity of things that have never been done before, and most of those things are not worth doing.} -- Jeremy Fox, \textit{Dynamic Ecology (2016)}~\cite{fox_how_2016}

>>>>

\textit{"There's an infinity of things that have never been done before, and most of those things are not worth doing."} -- Jeremy Fox, \textit{Dynamic Ecology}~\cite{fox_how_2016}

### 2017-04-09 Chapters/theory.tex
Correct quotes, add quote to chapter 3

\textit{Rather than propose a new theory or unearth a new fact, often the most important contribution a scientist can make is to discover a new way of seeing old theories or facts.} -- Richard Dawkins, \textit{The Selfish Gene}~\cite{dawkins_selfish_1976}, preface to 1989 edition.

>>>>

\textit{"Rather than propose a new theory or unearth a new fact, often the most important contribution a scientist can make is to discover a new way of seeing old theories or facts."} -- Richard Dawkins, \textit{The Selfish Gene}~\cite{dawkins_selfish_1976} (preface to 1989 edition).
